Bioverse: Origins of Life

### 2024-07-09 src/tex/ms.tex
save and cite some transit survey parameters
include new figure and describe it

@@

>>>>

... measure the maximum past \gls{NUV} flux with a precision of \var{nautilus_max_nuv} and the instellation that a planet receives with a precision of \var{nautilus_S}.

@@

\begin{figure}
    \script{inhabited_aafo_nuv_thresh.py}
    \begin{centering}
        \includegraphics[width=\hsize]{figures/inhabited_aafo_nuv_thresh}
        \caption{Fraction of inhabited planets for different threshold \gls{NUV} fluxes under the UV hypothesis if the abiogenesis rate is \var{f_life}.}
        \label{fig:inhabited_aafo_nuv_thresh}
    \end{centering}
\end{figure}
Figure \ref{fig:inhabited_aafo_nuv_thresh} shows the fraction of inhabited planets under the UV hypothesis for different threshold \gls{NUV} fluxes and for a high abiogenesis rate of \var{f_life}.
This fraction decreases sharply with increasing threshold flux, as fewer planets receive sufficient \gls{NUV} flux for abiogenesis.
For the FGK sample, the fraction of inhabited planets drops at lower threshold fluxes than for the M dwarf sample.
